Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
changed chunk options
include=FALSE for code chunks also present within the data/appendix from original report authors

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

#install_version("shapes", version = "1.2.3", repos = "http://cran.rstudio.com/") #"http://cran.us.r-project.org")
library(shapes) # shapes 1.2.3

@@

# Heirarchical Cluster Analysis of Havor lance dimensions
totalhc <-hclust(dist(total[,(c(1,5:11))]), "average")  # The cluster analysis is performed
totalhc1<-as.dendrogram(totalhc)                        # The cluster analysis results are converted into a dendrogram object
plot(totalhc1)                                          # Plots the resulting dendrogram object
```

```{r analysis 2, include=TRUE}

@@

```{r plotting digitized specs, include=TRUE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#
                          #### 6. PLOTTING DIGITISED SPECIMENS ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#

@@

```{r GPA, include=TRUE}

@@

```{r plotting GPA, include=TRUE}

@@

```{r check size vs shape, include=TRUE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
                          #### 9. ALLOMETRY: CHECKING IF SHAPE IS RELATED TO SIZE ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-

@@

```{r test mean shape diff, include=TRUE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
                          #### 10. TESTING FOR MEAN SHAPE DIFFERENCE: HOTELLING T^2 STATISTIC AND GOODALL F STATISTIC ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-

@@

```{r ANOVA test, include=TRUE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#
                          #### 11. PROCRUSTES ANALYSIS OF VARIANCE (ANOVA) ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#

@@

```{r PCA, include=TRUE}

@@

```{r JCA, include=TRUE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#
                          #### 13. HEIRARCHICAL CLUSTER ANALYSIS (HCA) OF GENERALISED PROCRUSTES ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#

@@

```{r bilateral symmetry, include=TRUE}

@@

ggpairs(lances_M, columns = c('total_length', 'blade_length', 'socket_length', 'sock_bdiam', 'sock_sdiam', 'width', 'thickness'),  
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8v1.png"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
```

@@

install_version("shapes", version = "1.2.3", repos = "http://cran.rstudio.com/") #"http://cran.rstudio.com")
#install_version("shapes", version = "1.2.3", repos = "http://cran.rstudio.com/") #"http://cran.us.r-project.org")
library(shapes) # shapes 1.2.3

@@

# Heirarchical Cluster Analysis of Havor lance dimensions
#totalhc <-hclust(dist(total[,(c(1,5:11))]), "average")  # The cluster analysis is performed
#totalhc1<-as.dendrogram(totalhc)                        # The cluster analysis results are converted into a dendrogram object
#plot(totalhc1)                                          # Plots the resulting dendrogram object
```
```{r analysis 1.1, include=FALSE}
# Heirarchical Cluster Analysis of Havor lance dimensions
# The cluster analysis is performed
totalhc <-hclust(dist(total[,(c(1,5:11))]), "average")
# The cluster analysis results are converted into a dendrogram object
totalhc1<-as.dendrogram(totalhc)                      
```
```{r analysis 1.2, include=TRUE}
# Plots the resulting dendrogram object
plot(totalhc1)
```
```{r analysis 2, include=FALSE}

@@

```{r plotting digitized specs, include=FALSE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#
                          #### 6. PLOTTING DIGITISED SPECIMENS ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#

@@

```{r GPA, include=FALSE}

@@

```{r plotting GPA, include=FALSE}

@@

```{r check size vs shape, include=FALSE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
                          #### 9. ALLOMETRY: CHECKING IF SHAPE IS RELATED TO SIZE ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-

@@

```{r test mean shape diff, include=FALSE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
                          #### 10. TESTING FOR MEAN SHAPE DIFFERENCE: HOTELLING T^2 STATISTIC AND GOODALL F STATISTIC ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-

@@

```{r ANOVA test, include=FALSE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#
                          #### 11. PROCRUSTES ANALYSIS OF VARIANCE (ANOVA) ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#

@@

```{r PCA, include=FALSE}

@@

```{r JCA, include=FALSE}
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#
                          #### 13. HEIRARCHICAL CLUSTER ANALYSIS (HCA) OF GENERALISED PROCRUSTES ----
                          #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#

@@

```{r bilateral symmetry, include=FALSE}

@@

#Copied to try to adjust to get to knit in Thomas's env
#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
#ggpairs(lances_M, columns = c('total_length', 'blade_length', 'socket_length', 'sock_bdiam', 'sock_sdiam', 'width', #'thickness'),  
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() +
#        ggsave(here("Images","replication_fig_8v1.png"))
